---
title: "Nonlinearity Assignment for Soc 413/513"
author: "Your Name Here"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, 
                      error = FALSE)
# load required libraries
source("check_packages.R")
```

```{r load-data, include=FALSE}
# load the analytical datam named `worldbank`
load(here("output","worldbank.RData"))
```

In this report, you should explore the relationship between GDP per capita and CO2 emissions per capita in a country using 2018 data from the World Bank. The analytical dataset is named `worldbank` and has only these two variables. You should focus on the following issues:

* Addressing non-linearity in the relationship between these two variables. 
* Addressing iid violations such as heteroskadasticity (watch for cone shapes!).

In your analysis, you should treat GDP per capita as the independent variable (i.e. the variable on the x-axis). Your analysis should include:

* Graphical exploration of the relationship, and text description of what this graphical exploration reveals.
* A final model which bests fit the underlying functional form and a description of what that model tells you about the relationship.

You should create new code chunks as need to do your analysis. Use one code chunk per figure. 
