---
title: "Nonlinearity Assignment for Soc 413/513"
author: "Your Name Here"
format: pdf
execute:
  echo: true
  message: false
  warning: false
  error: false
---

```{r}
#| label: load-libraries
#| include: false
source("check_packages.R")
```

```{r}
#| label: load-data
#| include: false
load(here("output","worldbank.RData"))
```

In this report, you should explore the relationship between GDP per capita and CO2 emissions per capita in a country using 2018 data from the World Bank. The analytical dataset is named `worldbank` and has only these two variables. You should focus on the following issues:

* Addressing non-linearity in the relationship between these two variables. 
* Addressing iid violations such as heteroskedasticity (watch for cone shapes!).

In your analysis, you should treat GDP per capita as the independent variable (i.e. the variable on the x-axis). Your analysis should include:

* Graphical exploration of the relationship, and text description of what this graphical exploration reveals.
* A final model which bests fit the underlying functional form and a description of what that model tells you about the relationship.

You should create new code chunks as need to do your analysis. Use one code chunk per figure. 

Below, I provide some starter code chunks for making a figure and a model table, but you should adjust as needed for your case.

```{r}
#| label: fig-template
#| fig-cap: A Caption

# Code for the figure below. You should change the label from "fig-template" to
# something relevant but it should start with "fig-". You can then reference
# this figure in the tex with @fig-whatever-you-called-it

# Each figure should go in a separate code chunk.
# replace this code with a real figure
ggplot(mtcars, aes(x=cyl, y=mpg))+
  geom_point()+
  theme_bw()
```


```{r}
#| label: tbl-reg
#| tbl-cap: A Caption
#| results: asis

# build your models here - change these
model1 <- lm(mpg~cyl+disp, data=mtcars)
model2 <- lm(mpg~cyl+disp+hp, data=mtcars)
model3 <- lm(mpg~cyl+disp+hp+wt, data=mtcars)

#to print to screen replace texreg with screenreg
texreg(list(model1, model2, model3),
       #uncomment next line to add nice labels to independent variables
       #custom.coef.names = c("Covariate labels here"),
       digits = 3,
       caption.above=TRUE, 
       include.rsquared=TRUE,
       include.adjrs=FALSE,
       include.nobs=TRUE,
       include.rmse=FALSE)
```
